Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-04 paper/ms.tex
minor updates to the abstract

\begin{abstract}
We use cosmological N-body simulations to find the characteristic mass
of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
redshift of $z=3.1$. The method is based on matching the statistics
for the number density between mock and observed fields. The mock
catalogs are constructed using a simple model where a dark matter halo
can only host one LAE with a probability $f_{\rm occ}$ if its mass is
found withing a certain range mass range delimited by two threshold
values, $M_{\rm min}$ and $M_{\rm max}$. We find that the most of the models that
are consistent the observed cosmic variance statistics are those with
halo masses in the range $10.5 < \log_{10} M_{\rm  min}/hMsun < 11.5$
and $\log_{10} M_{\rm max}/\hMsun < 13.5$ with and occupation fraction
that scales as $f_{\rm occ}=$. We explore three additional constraints
to narrow down these range: the number of mocks consistent with 
observations, observational constraints on the occupation fraction and
the angular correlation function. These three conditions narrow down
the space parameter to $10.1\leq M_{\rm min}\leq11.0$ and
$10.2\leq M_{\rm max}\leq12.0$, $0.1\leq_{\rm occ}\leq 0.2 $. 
 We make available the mock data for the best models in a public repository. 
 Implications for galaxy formation models? 
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}
\end{center}
\caption{Left: The fitted parameters  ($\theta_{0}$ vs $\gamma$) of the 
mean ACF  assuming a powerlaw behavior. Each blue dot corresponds to a
match-model while the green dot represent the powerlaw fit of the observational
ACF reported by \cite{Hayashino2004}.  The error bars represents the dispersion
in each parameter over all the mock surveys for a given model and dispersion due
to the observational error for the measured ACF by \cite{Hayashino2004}. Rigth: 
$\theta_{0}$ vs $M_{min}$. The date is subdivided into two blocks $M_{max}<12.0$ 
(blue) and $M_{max}>12.0$ (green). The red rectangle includes the region within
models are consisted with the observational angular-correlation lenght
($15<\theta_{0}<23$) as it can be deduced from the left panel. \label{figure:correlation_parameters} }  
\end{figure*}

>>>>

\begin{abstract}
We use cosmological N-body dark matter only simulations to constrain the
characteristic mass of dark matter halos hosting Lyman-Alpha Emitting
(LAE) galaxies at a redshift of $z=3.1$. The method is based on
matching the statistics for the number density between mock and
observed fields. The mock fields are constructed using a simple model
where a dark matter halo can only host one LAE with a probability
$f_{\rm occ}$ if its mass is found withing a certain range mass range
delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. 
We also maximize the number of mocks surveys consistent with
observations and impose consistency with the angular correlation
function. Under these conditions we find that LAEs are preferentially
hosted by halos in very narrow mass ranges less than 0.5 dex in width,
with the minimum mass $10\leq \log_{10}M_{\rm min}\leq 10.9$ and the
occupation fraction $f_{\rm   occ}\leq 0.2$.  Our finding suggest that
the most massive dark matter halos at that epoch do not host the
brightest LAEs. This also gives support to observational evidence that
says that only a small fraction of star forming galaxies can be
actually detected as LAEs.
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}
\end{center}
\caption{Left: The fitted parameters  ($\theta_{0}$ vs $\gamma$) of the 
mean ACF  assuming a powerlaw behavior. Each blue dot corresponds to a
match-model while the green dot represent the powerlaw fit of the observational
ACF reported by \citet{Hayashino2004}.  The error bars represents the dispersion
in each parameter over all the mock surveys for a given model and dispersion due
to the observational error for the measured ACF by \citet{Hayashino2004}. Rigth: 
$\theta_{0}$ vs $M_{min}$. The date is subdivided into two blocks $M_{max}<12.0$ 
(blue) and $M_{max}>12.0$ (green). The red rectangle includes the region within
models are consisted with the observational angular-correlation lenght
($15<\theta_{0}<23$) as it can be deduced from the left
panel. \label{figure:correlation_parameters}} 
\end{figure*}
